`flippant` -- An `R` package for the automated  analysis of dithionite

### 2015-09-17 inst/manuscript/manuscript.rmd
Finish a first draft of the Data Analysis flow;

Based on @menon_opsin_2011 and @goren_constitutive_2014, <CHECK THAT THERE'S INFO IN THE LATTER> data is processed as 
follows. Input is format checked and defaults are injected for facultative 
parameters/columns as appropriate. Fluorescence spectra are parsed, including 
determination of when dithionite was added to the sample using `wmtsa`-supplied
methodology <CITE AND MORE DETAIL> and resetting the acquisition time 
accordingly. The zero time point henceforth corresponds to the time of addition. 
Pre-dithionite-addition baseline fluorescence $F_{\text{baseline}}$ is 
determined for each spectrum by averaging (median) over the ten values preceding
dithionite addition. Post-dithinonite-addition minimum fluorescence 
$F_{\text{min}}$ is analogously calculated from the last ten datapoints after 
the default 400 s or the timepoint of measurement supplied by the user in the 
parameter file. $F_{\text{min}}$ is volume-corrected based on supplied reaction 
volumes
with and without dithionite and for each spectrum/datapoint a fluorescence 
reduction is calculated as follows:
$$
y_{\text{raw}} = 1 - \frac{F_{\text{min}}}{F_{\text{baseline}}}
$$
<!--
Data are split for parallel treatment using a combined Experimental Series/Experiment identifier (see above).

A Relative Fluorescence Reduction is calculated in comparison to the liposomes-only/no-protein control).

A Protein per Phospholipid (mg/mmol) ratio (PPR) is calculated.

A probability for a liposome holding ≤ 1 scramblase molecules is calculated using

(y - y0)/(ymax - y0)

where y is the Relative Fluorescence Reduction and y0 is the Relative Fluorescence Reduction in an experiment without addition of protein extract. Depending on the scaleTo parameter, ymax is either the maximal Relative Fluorescence Reduction in the series (scaleTo = "data") or derived from a mono-exponential fit to the data (scaleTo = "model"). The latter (default) is a precaution for the case where the protein/phospholipid titration did not reach the plateau of the saturation curve.

A monoexponential curve is fitted unsig nlxb to either

p(≤ 1) = b - c*exp(-PPR/a)

(if forceThroughOrigin = FALSE) or

p(≤ 1) = b * (1 - exp(-PPR/a))

(if forceThroughOrigin = TRUE).

Data split apart above are recombined and a ggplot object is assembled with the following layers:

Lines (geom_line) representing the monoexponential fit(s). color is used to differentiate Experimental Series.

Segments (geom_segment) representing the PPR at which the fit constant a is equal to PPR. This tau value has the implication that at this PPR all vesicles on average have one scramblase and 63% have one or more (i.e. are active). color is used to differentiate Experimental Series.

Points (geom_point) representing the corresponding datapoints. color is used to differentiate Experimental Series.

Plots are finally facet_wraped by Experiment and labels adjusted cosmetically.-->

>>>>

Based on @menon_opsin_2011 and @goren_constitutive_2014, data is processed as 
follows. Input is format checked and defaults are injected for facultative 
parameters/columns as appropriate. Fluorescence spectra are parsed, including 
determination of when dithionite was added to the sample using peak detection by
continuous wavelet transformation as implemented by the `wmtsa` `R` package 
[@percival_wavelet_2000;@constantine_wmtsa:_2013] and resetting the acquisition 
time accordingly. The zero time point henceforth corresponds to the time of 
addition. 
Pre-dithionite-addition baseline fluorescence $F_{\text{baseline}}$ is 
determined for each spectrum by averaging (median) over the ten values preceding
dithionite addition. Post-dithinonite-addition minimum fluorescence 
$F_{\text{min}}$ is analogously calculated from the last ten datapoints after 
the default 400 s or the timepoint of measurement supplied by the user in the 
parameter file. $F_{\text{min}}$ is volume-corrected based on supplied reaction 
volumes
with and without dithionite and for each spectrum/datapoint a fluorescence 
reduction is calculated as follows:
$$
y_{\text{raw}} = 1 - \frac{F_{\text{min}}}{F_{\text{baseline}}}
$$
<!--
Data are split for parallel treatment using a combined Experimental Series/Experiment identifier (see above).-->
A relative fluorescence reduction $y$ is calculated scaled to a (required) liposomes-only/no-protein control and the probability $P_{\geq 1}$ for a 
liposome to contain at least one scramblase molecules is calculated using
$$
P_{\geq 1} = \frac{(y - y_0)}{(y_{\text{max}} - y_0)}
$$
where $y$ is the relative fluorescence reduction for the proteoliposome 
measurement and $y_0$ for a measurement of protein-free liposomes. 
$y_{\text{max}}$ refers to either the maximal $y$ in the experiment or is 
derived from a monoexponential fit to the data (default) as a precaution for the 
case where the protein/phospholipid titration did not reach the plateau of the 
saturation curve. The behavior is adjustable using the `scaleTo` parameter of 
the corresponding functions (see below). Next a monoexponential curve is fitted
to the realtionship of $P_{\geq 1}$ to the protein to phospholipid ratio (PPR; 
(mg/mmol)), providing the scramblase-characterizing fit factor $\alpha$.
